Isomorphic Interpreters from Logically Reversible Abstract Machines

### 2012-03-16 iso-int/rc-iso-int.tex
one more fix

Our goal is to implement this abstract machine in {{langRevT}}, i.e., our
goal is to write a combinator {{c : nat * nat <-> nat * nat}} where {{nat}}
is an abbreviation for the recursive type {{@@x.1+x}}. The combinator should
map {{(n,0)}} to {{(0,n)}} by precisely mimicking the steps of the abstract
machine. Let us analyze this desired combinator {{c}} in detail starting from
its interface:

@@

The introduced {{trace}} feeds back related machine states. The
exposed start state essentially requires the initial value of {{n}} to
start the machine.

>>>>

Our goal is to implement this abstract machine in {{langRevT}}: We
start by writing a combinator {{c : nat * nat <-> nat * nat}} that
executes a `small step'. Here {{nat}} is an abbreviation for the
recursive type {{@@x.1+x}}. The combinator, when iterated, should map
{{(n,0)}} to {{(0,n)}} by precisely mimicking the steps of the
abstract machine. Let us analyze this desired combinator {{c}} in
detail starting from its interface:

@@

The introduced {{trace}} feeds back related machine states. The
exposed start state essentially requires the initial value of {{n}} to
start the machine and the exposed stop state returns any result values
that have been computed.
